---
title: "Fuzzy-Matcher-Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fuzzy-Matcher-Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Fuzzy Matcher Guide

## Introduction

Because of the Fuzzy Matchers GUI interface, the standard R function documentation is ill-suited to helping with its use. Instead this guide has been created to guide you through using this function.

## Data Prep

The first step of using the Fuzzy Matcher is to prepare the datasets you would like to match. The Fuzzy Matcher requires two different data frames as its input, with an optional key word. In this example, we will create two data frames and then match items between them.

### R setup

First we load the required packages. NutritionTools is this package, which contains Fuzzy Matcher, which we need. dplyr is a package which is widely used and contains many useful tools. It is also a dependency of NutritionTools, so should already be installed on your system. Because some of the data prep methods can be done with dplyr instead of base R, both methods will be shown - requiring it to be called now.


```{r eval = FALSE, setup}
library(NutritionTools)
library(dplyr)
```

